---
title: "Cabbages"
author: "Esteffani Maldonado"
date: "9/2/2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```
  
According to the box plot above, c52 has a higher amount of vitamin C than c39. By observing the box plot, we can see that the median of c52 is significantly higher than the median of c39. We can also see that the 25th percentile from the c52 method is still higher than the 75th percentile from the c39 method. It is clear that the cultivation method c52 is producing way more vitamin C than c39.  
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```
  
Now we can see that the mean amount of vitamin c produced by c39 is 51.5, and the mean amount produced by c52 is 64.4. This supports our claim that the c52 cultivation method produces more vitamin c than the c39 cultivation method.   
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
  
According to this data, our p-value is 0.00000003405. This means that if the null hypothesis were true, we would have a 0.00000003405 probability of achieving these results. This p-value is exceedingly low, meaning that we can reject the null hypothesis.   
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
The first step we took is understanding what kind of problem we were dealing with so we could know which helper file we would need. We compared two cultivation methods, which was our categorical variables, by how much vitamin c they produced respectively, which was our numerical variable. This meant that we would need to use the Numerical~Categorical helper file. We uploaded the file and then moved on to the graphical descriptive results. We placed out data on a box plot using the function boxplot(). Next, we imported a favstats function to view the exact means of how much vitamin c was produced by c39 and c52, respectively. Lastly, we used a t-test to calculate the p-value. The p-value was extremely low, which meant that we could reject the null hypothesis.   
  